---
title: "p8105_hw1_jl5548"
author: "J L"
date: "September 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1

The chunk below creates a data frame comprised of:
* a random sample of size 8 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 8
* a factor vector of length 8, with 3 different factor "levels"

```{r}
df = tibble(
  vec_numeric = rnorm(8),
  vec_logical = vec_numeric > 0,
  vec_char = c("s", "o", "m", "e", "c", "h", "a", "r"),
  vec_factor = factor(c("butterfly", "dream", "Zhuang", "dream", "butterfly", "dream", "Zhuang", "dream"))
)
```

The mean of the numeric vector is `r mean(df$vec_numeric)`.
The mean of the logical vector is `r mean(df$vec_logical)`.
The mean of the character vector is `r mean(df$vec_character)`.
The mean of the factor vector is `r mean(df$vec_factor)`.
As illustrated above, taking the mean of the numeric and logical vectors works, but taking the mean of the character and factor vectors does not work.


## Problem 2


```{r}

```

